---
title: "Accuracy by Difficulty Levels"
author: "Christian Medeiros Adriano"
date: "June 2, 2017"
output: html_document
---

<h2> Analysis of answer accuracy by the difficulty level of questions</h2>
<p>Are workers more accurate in their answers when they consider questions less difficult?</p>

```{r setup, echo=FALSE}
#Setup

library("ggplot2");

loadAnswers<- function(fileName){
  
  setwd("C://Users//chris//OneDrive//Documentos//GitHub//photinus-analytics//correlationGraphs//");
  data_all <- read.csv(fileName,header = TRUE,sep=",");
  dataf = data.frame(data_all);
  return(dataf);
}

dataf<- loadAnswers("answerList_photinus_data.csv");
#Check if total answers is 2580
#length(dataf$TP)

#Select TP, TN, FP, FN for the item
selectOutcomes <- function(df,lineNumbers){
  dataf_difficulty <- df [(lineNumbers) ,];
  TP <- sum(dataf_difficulty$TP);
  TN <- sum(dataf_difficulty$TN);
  FP <- sum(dataf_difficulty$FP);
  FN <- sum(dataf_difficulty$FN);
  outcome.df <- data.frame(TP,TN,FP,FN);
  return (outcome.df);
}

#Compute accuracy 
computeAccuracy<- function(df){
  return((df$TP+df$TN)/(df$TP+df$TN+df$FP+df$FN));
}

#Compute precision
computePrecision<- function(df){
  result<-(df$TP)/(df$TP+df$FP);
  if(is.nan(sum(result))){
    index<- is.nan(result);
    result[index]<-0;
  }
  return(result);
}

#Compute recall
computeRecall<- function(df){
  return((df$TP)/(df$TP+df$FN));
}

## Computes a table with statistics each level of difficulty
computeStats<- function(df,selection, filterName){
  
  dataframe <- data.frame(Difficulty=double(),Accuracy=double(), Precision=double(), Recall=double(), Answers=double() );
  
  for(i in 1:5){
    outcomesDF<- selectOutcomes(df,selection==i);
    dataframe[i,1]<-i;
    dataframe[i,2]<-computeAccuracy(outcomesDF);
    dataframe[i,3]<-computePrecision(outcomesDF);
    dataframe[i,4]<-computeRecall(outcomesDF);
    dataframe[i,5]<-sum(outcomesDF[1,]);
  }
  print(filterName);
  print(dataframe);
  message("Total answers:" , sum(dataframe$Answers));
  
  return(dataframe);
}

## Builds plots with multiple lines
plotMultiLine <- function(stats,title){
  
  multiplot <- ggplot(stats, aes(x=Difficulty),fill="Metrics") +
    geom_line(aes(y = Accuracy, colour="Accuracy")) + 
    geom_line(aes(y = Recall, colour = "Recall")) +
    geom_line(aes(y = Precision, colour = "Precision")) +
    ggtitle(title) +
    ylab(label="Metrics") + 
    xlab("difficulty") +
    scale_colour_manual("", 
                        breaks = c("Accuracy" ,"Recall","Precision"),
                        values = c("Accuracy"="blue","Recall"="black","Precision"="red"))+
    scale_y_continuous(limits = c(0, 1));
  
  return(multiplot);
}

plotSingleLine <- function(stats,title){
  
  singlePlot <- ggplot(stats, aes(x=Difficulty),fill="Metrics") +
    geom_line(aes(y = Accuracy, colour="Accuracy")) + 
    ggtitle(title) +
    ylab(label="Metrics") + 
    xlab("difficulty") +
    scale_colour_manual("", 
                        breaks = c("Accuracy"),
                        values = c("Accuracy"="blue"))+
    scale_y_continuous(limits = c(0, 1));
  return(singlePlot);
}

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

```

<h2> How do the accuracy of answers options (YES,NO) relate with the difficulty level of the questions?</h2>

```{r answerOption, echo=FALSE}
################################################################################
##### Analysis by Answer option (YES, NO)

## ALL answers
stats1<- computeStats(dataf,dataf$Answer.difficulty,"All Answers - difficulty");

## Only YES's
dataYES <- dataf [(dataf$Answer.option=="YES") ,];
stats2<- computeStats(dataYES,dataYES$Answer.difficulty,"Only YES Answers - difficulty");

## Only NO's
dataNO <- dataf [(dataf$Answer.option=="NO") ,];
stats3<- computeStats(dataNO,dataNO$Answer.difficulty,"Only NO Answers - difficulty");

#Plotting
# breaks =c("Accuracy" ,"Recall","Precision")
p1<- plotMultiLine(stats1,"All answers");
p2<- plotSingleLine(stats2,"Only Yes answers");
p3<- plotSingleLine(stats3,"Only No answers");
multiplot(p1, p2, p3, cols=2);
```

<p>For all metrics, answer accuracy is negatively proportionate to difficulty level (need to confirm that by computing correlation). </p>

<h2>How do the accuracy of answers by worker profession relate with the difficulty level of the questions? </h2>

```{r answerbyProfession, echo=FALSE}
################################################################################

#### WORKER PROFESSION
## Only PROFESSIONAL_DEVELOPERS
dataProf <- dataf [(dataf$Worker.profession=="Professional_Developer") ,];
stats1<- computeStats(dataProf,dataProf$Answer.difficulty,"Only PROFESSIONAL_DEVELOPERS - difficulty");

## Only HOBBYIST´S
dataProf <- dataf [(dataf$Worker.profession=="Hobbyist") ,];
stats2<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HOBBYIST - difficulty");

## Only GRADUATE_STUDENT´S
dataProf <- dataf [(dataf$Worker.profession=="Graduate_Student") ,];
stats3<- computeStats(dataProf,dataProf$Answer.difficulty,"Only GRADUATE_STUDENT - difficulty");

## Only Hobbyist´S
dataProf <- dataf [(dataf$Worker.profession=="Hobbyist") ,];
stats4<- computeStats(dataProf,dataProf$Answer.difficulty,"Only Hobbyist - difficulty");

## Only OTHER´S
dataProf <- dataf [(dataf$Worker.profession=="Other") ,];
stats5<- computeStats(dataProf,dataProf$Answer.difficulty,"Only OTHER - difficulty");

# breaks =c("Accuracy" ,"Recall","Precision")
p1<- plotMultiLine(stats1,"Professional Developers");
p2<- plotMultiLine(stats2,"Hobbyists");
p3<- plotMultiLine(stats3,"Graduate students");
p4<- plotMultiLine(stats4,"Undergraduate students");
p5<- plotMultiLine(stats5,"Others");
multiplot(p1, p2, p3, p4, p5, cols=3);
```

<p> As the charts above show, even across professions accuracy and difficulty follows are inversely proportionate.</p>

```{r answerbyJavaMethod, echo=FALSE}
#### JAVA METHOD
dataProf <- dataf [(dataf$FailingMethod =="HIT01_8") ,];
stats1<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT01_8 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT02_24") ,];
stats2<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT02_24 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT03_6") ,];
stats3<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT03_6 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT04_7") ,];
stats4<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT04_7 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT05_35") ,];
stats5<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT05_35 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT06_51") ,];
stats6<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT06_51 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT07_33") ,];
stats7<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT07_33 - difficulty");

dataProf <- dataf [(dataf$FailingMethod =="HIT08_54") ,];
stats8<- computeStats(dataProf,dataProf$Answer.difficulty,"Only HIT08_54 - difficulty");

# breaks =c("Accuracy" ,"Recall","Precision")

p2<- plotSingleLine(stats2,"HIT02_24");
p5<- plotSingleLine(stats5,"HIT05_35");
p7<- plotSingleLine(stats7,"HIT07_33");
p1<- plotSingleLine(stats1,"HIT01_8");
p3<- plotSingleLine(stats3,"HIT03_6");
p6<- plotSingleLine(stats6,"HIT06_51");
p8<- plotSingleLine(stats8,"HIT08_54");
p4<- plotSingleLine(stats4,"HIT04_7");

multiplot(p2, p5, p7, p1,cols=4);

multiplot(p3, p6, p8, p4, cols=4);
```
