---
title: "workerGroupByBugCoveringQuestion"
author: "Christian Medeiros Adriano"
date: "July 25, 2017"
output: html_document
---

#Do bug-covering questions receive more answers from professional developers than other questions?
#Are these differences statistically significant?

```{r setup, include=FALSE}
library(dplyr);
source("C://Users//chris//OneDrive//Documentos//GitHub//photinus-analytics//loadAnswers.R");

#Bug covering question ID's
bugCoveringID<- c(1,4,10,14,20,23,30,32,55,56,57,58,59,72,73,77,84,92,95,97,102,104,115,119,123);

dataf =loadAnswers();

##function to count the numer of workers with profession X for each question
countItem<- function(dataf, profession){
  subset_df <-subset(dataf,select= c(Worker.profession)); ##extract only the column Worker.profession)
  subset_df <- data.frame(subset_df); 
  
  if(length(profession)==0){
    itemCount<- rowSums(subset_df==profession); ##Row with ones when profession match, otherwise zero
  }
  else{
    itemCount<- 1; #c(1:dim(subset_df)[1]);
  }
    subset_df["itemCount"] <- itemCount;
  subset_df["Question.ID"] <- dataf$Question.ID;
   
 ## subset_df <-subset(subset_df,select= c(Question.ID,itemCount));##select only the rows with 
  question_by <- group_by(subset_df,Question.ID);
  summaryTable <- summarize(question_by,sum(itemCount));
  colnames(summaryTable)<-c("QuestionID","itemCount");
  
  return(summaryTable);
}


``` 




### Actual analysis




### Professional Developers
#Can we assert that bug covering questions have more professional developers answers on average? 
```{r analysis1, echo=FALSE}
profession<-"Professional_Developer";
professionList<-countItem(dataf,profession);
bugCoveringList<- professionList[(professionList$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- professionList[!(professionList$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); ####Normal W = 0.94579, p-value = 0.2011
shapiro.test(not_bugCoveringList$itemCount); ####Not normal W = 0.94811, p-value = 0.0004707


wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1330, p-value = 0.8587

#Wilcox non-parametric test could not show that the average number of answers to bug-covering and non-bug covering 
#questions are distinct. However, we should be cautions that the lack of evidence of an effect is not proof that of lack of effect.

##############################################################################
## PROFESSION ################################################################
############################################################################
###  FILTER-OUT "Professional_Developer","Hobbyist","Other"
#OK, filter does not cause bias
```{r analysis3, echo=FALSE}
non_students<- dataf[!(dataf$Worker.profession %in% c("Professional_Developer","Hobbyist","Other")),];
non_students<-countItem(non_students,""); 

bugCoveringList<- non_students[(non_students$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- non_students[!(non_students$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Not Normal W = 0.90395, p-value = 0.02239
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.94641, p-value = 0.0003637


wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1196.5, p-value = 0.5333

#Wilcox non-parametric test could not show that the average number of answers to bug-covering and non-bug covering 
#questions are distinct. However, we should be cautions that the lack of evidence of an effect is not proof that of lack of effect.

############################
### FILTER-OUT Undergraduate_Student,Graduate_Student, hobbyists, others 
#OK, filter does not cause bias
```{r analysis4, echo=FALSE}
professionList<- dataf[!(dataf$Worker.profession %in% c("Undergraduate_Student","Graduate_Student","Hobbyist","Other")),];

professionList<-countItem(professionList,""); 

bugCoveringList<- professionList[(professionList$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- professionList[!(professionList$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Not Normal W = 0.94579, p-value = 0.2011
shapiro.test(not_bugCoveringList$itemCount); #Not normalW = 0.94811, p-value = 0.0004707


wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1330, p-value = 0.8587

#Wilcox non-parametric test could not show that the average number of answers to bug-covering and non-bug covering 
#questions are distinct. However, we should be cautions that the lack of evidence of an effect is not proof that of lack of effect.

############################
### FILTER-OUT Graduate_Student, hobbyists, others 
#OK, filter does not cause bias
```{r analysis5, echo=FALSE}
professionList<- dataf[!(dataf$Worker.profession %in% c("Graduate_Student","Hobbyist","Other")),];

professionList<-countItem(professionList,""); 

bugCoveringList<- professionList[(professionList$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- professionList[!(professionList$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Normal W = 0.94106, p-value = 0.1566
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.9589, p-value = 0.002643


wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1337.5, p-value = 0.8231

#Wilcox non-parametric test could not show that the average number of answers to bug-covering and non-bug covering 
#questions are distinct. However, we should be cautions that the lack of evidence of an effect is not proof that of lack of effect.

############################
### FILTER-OUT Undergraduate_Student,Graduate_Student, others 
#OK, filter does not cause bias
```{r analysis6, echo=FALSE}
professionList<- dataf[!(dataf$Worker.profession %in% c("Undergraduate_Student","Graduate_Student","Other")),];

professionList<-countItem(professionList,""); 

bugCoveringList<- professionList[(professionList$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- professionList[!(professionList$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Not Normal W = 0.90256, p-value = 0.02086
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.95576, p-value = 0.001575


wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1477.5, p-value = 0.2851

#Wilcox non-parametric test could not show that the average number of answers to bug-covering and non-bug covering 
#questions are distinct. However, we should be cautions that the lack of evidence of an effect is not proof that of lack of effect.




##############################################################################
## SCORE #####################################################
############################################################################

### worker score = 100%
#Not OK, filter injected bias
```{r analysis7, echo=FALSE}
workers_100<- dataf[(dataf$Worker.score == 5),];

workers_100<-countItem(workers_100,""); 

bugCoveringList<- workers_100[(workers_100$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- workers_100[!(workers_100$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Not Normal W = 0.88385, p-value = 0.008305
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.95902, p-value = 0.002696

mean(bugCoveringList$itemCount)
#9.48
mean(not_bugCoveringList$itemCount)
#8.5

wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE, conf.int = TRUE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1643, p-value = 0.03867
#alternative hypothesis: true location shift is not equal to 0
#95 percent confidence interval:
#  3.075891e-05 1.999998e+00
#sample estimates:
#  difference in location 
#0.9999684 

#Wilcox non-parametric test SHOWED that the average number of answers for bug covering and non-bug covering are distinct with a 95% confidence interval.
#Moreover, bug-covering received more answers in average. This unbalance implies that we cannot trust that the filter is actually fair. However, the difference
#between the two median number of answers is small (approximately one answer of difference). 
#Therefore, we kept the outcome of the filter but we marked it with a star.

#####################################
### worker score = 100% or 80%
#Not OK, filter injected bias
```{r analysis8, echo=FALSE}
workers_100_80<- dataf[(dataf$Worker.score %in% c(5,4)),];

workers_100_80<-countItem(workers_100_60,""); 

bugCoveringList<- workers_100_60[(workers_100_60$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- workers_100_60[!(workers_100_60$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Not Normal W = 0.90188, p-value = 0.02016
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.96726, p-value = 0.01121

mean(bugCoveringList$itemCount)
#10.28
mean(not_bugCoveringList$itemCount)
#11.33654

wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE, conf.int = TRUE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 924.5, p-value = 0.0238
#alternative hypothesis: true location shift is not equal to 0
#95 percent confidence interval:
#  -1.999977e+00 -4.944597e-05
#sample estimates:
#  difference in location -1.000029 

#Wilcox non-parametric test SHOWED that the average number of answers for bug covering and non-bug covering are distinct with a 95% confidence interval.
#Moreover, bug-covering received more answers in average. This unbalance implies that we cannot trust that the filter is actually fair. However, the difference
#between the two median number of answers is small (approximately one answer of difference). 
#Therefore, we kept the outcome of the filter but we marked it with a star.


#########################################################

#####################################
### worker score = 80% or 60%
#Not OK, filter injected bias
```{r analysis8, echo=FALSE}
workers_80_60<- dataf[(dataf$Worker.score %in% c(4,3)),];

workers_80_60<-countItem(workers_80_60,""); 

bugCoveringList<- workers_80_60[(workers_80_60$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- workers_80_60[!(workers_80_60$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Not Normal W = 0.90188, p-value = 0.02016
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.96726, p-value = 0.01121

mean(bugCoveringList$itemCount)
#10.28
mean(not_bugCoveringList$itemCount)
#11.33654

wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE, conf.int = TRUE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 924.5, p-value = 0.0238
#alternative hypothesis: true location shift is not equal to 0
#95 percent confidence interval:
#  -1.999977e+00 -4.944597e-05
#sample estimates:
#  difference in location -1.000029 

#Wilcox non-parametric test SHOWED that the average number of answers for bug covering and non-bug covering are distinct with a 95% confidence interval.
#Moreover, bug-covering received more answers in average. This unbalance implies that we cannot trust that the filter is actually fair. However, the difference
#between the two median number of answers is small (approximately one answer of difference). 
#Therefore, we kept the outcome of the filter but we marked it with a star.


#########################################################


##############################################################################
## PROFESSION AND SCORE #####################################################
############################################################################
#Not OK, filter injected bias

### non-students score = 100% (Professional_Developers, Hobbyists, and Others)
```{r analysis9, echo=FALSE}
non_students<- dataf[(dataf$Worker.profession %in% c("Professional_Developer","Hobbyist","Other")),];
non_students<- non_students[(non_students$Worker.score == 5),];

non_students<-countItem(non_students,""); 

bugCoveringList<- non_students[(non_students$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- non_students[!(non_students$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Normal W = 0.95015, p-value = 0.2527
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.96348, p-value = 0.005757

mean(bugCoveringList$itemCount)
#7.36
mean(not_bugCoveringList$itemCount)
#6.27

wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE, conf.int = TRUE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1715, p-value = 0.01214
#alternative hypothesis: true location shift is not equal to 0
#95 percent confidence interval:
#  3.068510e-06 1.999979e+00
#sample estimates difference in location = 1.000018 

#Wilcox non-parametric test SHOWED that the average number of answers for bug covering and non-bug covering are distinct with a 95% confidence interval.
#Moreover, bug-covering received more answers in average. This unbalance implies that we cannot trust that the filter is actually fair, therefore the 
#outcome of this filter cannot be un For this reason, we cannot 

##############################################
### FILTER OUT (all students) && (non-students below 60%)
##leave only non-students with score 100% and 80%
#OK, filter does not cause bias

```{r analysis10, echo=FALSE}
non_student_100_80<- dataf[((dataf$Worker.profession %in% c("Professional_Developer","Hobbyist","Other")) & dataf$Worker.score %in% c(4,5)),];

non_student_100_80<-countItem(non_student_100_80,""); 

bugCoveringList<- non_student_100_80[(non_student_100_80$QuestionID %in% bugCoveringID),];
not_bugCoveringList<- non_student_100_80[!(non_student_100_80$QuestionID %in% bugCoveringID),];
```
shapiro.test(bugCoveringList$itemCount); #Normal W = 0.93489, p-value = 0.1128
shapiro.test(not_bugCoveringList$itemCount); #Not normal W = 0.96072, p-value = 0.003591

mean(bugCoveringList$itemCount) #11.28
mean(not_bugCoveringList$itemCount) #10.49

wilcox.test(bugCoveringList$itemCount,not_bugCoveringList$itemCount, alternative= "two.sided", paired=FALSE, conf.int = TRUE);
#data:  bugCoveringList$itemCount and not_bugCoveringList$itemCount
#W = 1547, p-value = 0.1384

#Wilcox non-parametric test COULD NOT SHOW that the average number of answers for bug covering and non-bug covering are distinct with a 95% confidence interval.
