---
title: "Were some questions answered by more experienced workers?"
author: "Christian Medeiros Adriano"
date: "May 12, 2017"
output: html_document
---


### The goal of the study
  <p>Distribution of worker skill level across questions has the potential to bias the outcomes of the larger crowdsourcing task. The reason is that software faults can be overlooked if they are covered by questions* that were mostly answered by lower skill workers. </p>

<p>*Each question covers a certain number of source code lines. Questions have the following format:"Do you believe the source code between lines 35 and 45 is related to the described failure?"</p>
  
<p>  Therefore, my goal is to investigate how worker skill level is distributed across questions. Worker skill level was measured by the following three attributes. 
  <du>
  <li>Test score: workers received a score (zero to five) after performing a computer programming test used to filter
   out workers without enough programming knowledge. Workers who scored 2 or less were not allowed to participate.
  <li>Years of programming experience: Worker quality can also be measured by years of programming experience, which is an information self-declared by workers befote they take any test. 
   <li>Profession: worker profession is also an indicator of quality. Professions consisted of professional programmers, hobbyists, graduate students, undergraduate students, and others.
   </du>

###Focus of the current analysis
<p>The current analysis focuses only on the <b>worker´s years of experience</b>.</p>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr);
library(ggplot2);
source("C://Users//chris//OneDrive//Documentos//GitHub//photinus-analytics//loadAnswers.R");
source("C://Users//chris//OneDrive//Documentos//GitHub//photinus-analytics//multiplot.R");

dataf =loadAnswers();

#summary(dataf$Worker.yearsOfExperience)

##function to count the number of YoE entries that fall within start (inclusive) and end (exclusive)
countYoE<- function(dataf, startYear, endYear){
  subset_df <-subset(dataf,select=c(Worker.yearsOfExperience));
  subset_df <- data.frame(subset_df); 
  
  yearCount<- rowSums(subset_df>=startYear & subset_df<endYear);
  subset_df["yearCount"] <- yearCount;
  subset_df["Question.ID"] <- dataf$Question.ID;

  subset_df <-subset(subset_df,select= c(Question.ID,yearCount));
  question_by <- group_by(subset_df,Question.ID);
  summaryTable <- summarize(question_by,sum(yearCount));
  colnames(summaryTable)<-c("QuestoinID","yearCount");
 
  return(summaryTable);
}

#List the workers and respective years of experience
listWorkerYoE<- function(dataf){
  workerYoE_vector<-{};
  #colnames(workersYoE_vec)<-c("WorkerID","YoE");
  size<-length(dataf$Worker.ID);
  for(i in 1:size){
    workerYoE_vector[dataf$Worker.ID[i]]<-dataf$Worker.yearsOfExperience[i];
  }
  
  #Remove NA's 
  workerYoE_vector<- workerYoE_vector[!is.na(workerYoE_vector)]
  
  return(workerYoE_vector);
}

```

<p> First let's see how the workers are distributed in terms of years of experience.</p>

```{r histogram, echo=FALSE}
workersYoE_vec <- listWorkerYoE(dataf);
dt<-data.frame(workersYoE_vec);
dt["worker"]<-c(1:length(dt));
colnames(dt)<-c("years_of_experience","worker");

summary(dt);

#clean-up NA's
years_of_experience.mean<- mean(dt$years_of_experience, na.rm=T);

title<- paste("Fig.1 - Histogram of years of experience in computer programming (red line is the mean)");
ggplot(dt,aes(x=years_of_experience))+
  geom_histogram(binwidth = 0.1) +
  geom_vline(data=dt, aes(xintercept=years_of_experience.mean),linetype="dashed", size=1, colour="red")+
  ggtitle(title) +
  theme(plot.title = element_text(size = 10))+
  labs(y="number of workers", x="years of experience");


```
<p> We can obsreve that workers concentrated their information on multiples of 5 and 10. </p>
<p> Since the distribution is very skewed (to the right in this case), the average is not a good representation of the data. The alterantive in these cases is to look at the quartiles, which are shown in the boxplot below.</p>

```{r boxplot, echo=FALSE}

title<- paste("Fig.2 - Boxplot of years of experience in computer programming");
ggplot(dt,aes(y=years_of_experience, x=worker))+ geom_boxplot()+
   stat_summary(fun.y=mean, fun.ymax=max, geom="point", shape=5, size=4)+
  ggtitle(title) +
   theme(plot.title = element_text(size = 10))+
   labs(x="workers", y="years of experience");

summary(dt$years_of_experience);
```

<p> Bloxplot shows that half of the data points are bewlo 5 years of experience. 25% are between 5 and 10 years of experience. </p>


<p> Therefore, in order to investigate the distribute of years of experience across questions, I selected the following four intervals: below 2 years, from 2 to 5 years, from 5 to 10, and above 10 years of experience.</p>



```{r analysis, echo=FALSE}

#Compute distribution of years of experience below 5.


fontSize<-10;

startYear<-0;
endYear<-2;
dt<-countYoE(dataf,startYear,endYear);
title<- paste("Fig.1 Workers per question, YoE=[",startYear,",", endYear,"]");
p1<-ggplot(dt,aes(x=yearCount))+
  geom_histogram(binwidth = 0.2) +
  ggtitle(title) +
  theme(plot.title = element_text(size = fontSize))+
  labs(y="question count", x="workers per question");

startYear<-2;
endYear<-5;
dt<-countYoE(dataf,startYear,endYear);
title<- paste("Fig.2 Workers per question, YoE=[",startYear,",", endYear,"]");
p2<-ggplot(dt,aes(x=yearCount))+
  geom_histogram(binwidth = 0.2) +
  ggtitle(title) +
  theme(plot.title = element_text(size = fontSize))+
  labs(y="question count", x="workers per question");

startYear<-5;
endYear<-10;
dt<-countYoE(dataf,startYear,endYear);
title<- paste("Fig.3 Workers per question, YoE=[",startYear,",", endYear,"]");
p3<-ggplot(dt,aes(x=yearCount))+
  geom_histogram(binwidth = 0.2) +
  ggtitle(title) +
  theme(plot.title = element_text(size = fontSize))+
  labs(y="question count", x="workers per question");

startYear<-10;
endYear<-51;
dt<-countYoE(dataf,startYear,endYear);
title<- paste("Fig.4 Workers per question, YoE=[",startYear,",", endYear,"]");
p4<-ggplot(dt,aes(x=yearCount))+
  geom_histogram(binwidth = 0.2) +
  ggtitle(title) +
  theme(plot.title = element_text(size = fontSize))+
  labs(y="question count", x="workers per question");

multiplot(p1,p2,p3,p4,cols=2)

```

<p> As we can see, workers are not equally distributed across questions. This suggests that some questions might have been overlooked by having been answered by less experienced workers. As in the case of Figures 2, 3 and 4, some questions can have almost 5 times more experience workers than other questions. </p>